A Dependently Typed Multi-Stage Calculus

### 2019-08-24 text/formal-defnition.tex
Change the style of syntax.
Fix "Typing rules for a multi-stage calculus"

{%\small
\begin{align*}
    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
    \textrm{kinds}             &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
    \textrm{types}             &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
    %     \textrm{Constants}       &   &                          & c                                                                                                          \\
    \textrm{terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
                               &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ A \mid \%_\alpha M        \\
    \textrm{signatures}         &  & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                               \\
    \textrm{type env.} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
\end{align*}
}
% \AI{Add $M\,\alpha$ to terms.}

@@

% Typing rules for a multi-stage calculus
The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are constructs for multi-stage progarmming.
\TTB{} and \TTBL{} are the same as \LTP, as we explained in Section \ref{sec:informal-overview}.
The rule \TGen{} for stage abstraction is straightforward.
The condition $\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensures that the scope of $\alpha$ is in $M$.
The rule \TIns{} is for applications of stages to stage abstractions.
% \TIns{} is mainly used when we run a code value or rename a stage variable in the body of an abstraction.
The rule \TCsp{} is for CSP, which means that,
if term $M$ is of type $\tau$ at stage $A$, then $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.
Note that CSP is also applied to the type \(\tau\) (although it is implicit) in the conclusion.  Thanks to implicit CSP, the typing rule is the same as \LTP.

>>>>

{%\small
\begin{align*}
    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
    \textrm{kinds}             &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
    \textrm{types}             &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
    %     \textrm{Constants}       &   &                          & c                                                                                                          \\
    \textrm{terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ N \mid \TB_\alpha M                   \\
                               &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ A \mid \%_\alpha M        \\
    \textrm{signatures}         &  & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                               \\
    \textrm{type env.} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
\end{align*}
}
% \AI{Add $M\,\alpha$ to terms.}

@@

% Typing rules for a multi-stage calculus
The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are constructs for
multi-stage progarmming. \TTB{} and \TTBL{} are the same as \LTP, as we
explained in Section \ref{sec:informal-overview}. The rule \TGen{} for stage
abstraction is straightforward. The condition
$\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensures that the scope of $\alpha$
is in $M$, and avoids capturing variables in the rest of the judgments. The
rule \TIns{} is for applications of stages to stage abstractions. The rule
\TCsp{} is for CSP, which means that, if term $M$ is of type $\tau$ at stage
$A$, then $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$. Note that CSP
is also applied to the type \(\tau\) (although it is implicit) in the
conclusion. Thanks to implicit CSP, the typing rules are the same as in \LTP.
